maxent model avec xvalidation (year-based test training)

### 2019-05-10 src/maxent_avec_xvalidation.Rmd
minor adjustment for year variation (presence with data)

select month
```{r month of interest -change}
mthna <- "may"
mthno <- "5"
```

@@

```{r remove na vals}
prback <- na.omit(prback)
```

@@

```{r train and test inc AIC for reg val}
modelmonth <- cbind(paste0(mthna ,unique(prback$year)))
aicetc <- read.csv("../data/env/AICcCalculations.csv", header = TRUE) #pre-created csv file
betavallist <- cbind(aicetc$regularization)

@@

@@

  if (yr == "2006"){
    betaval <- 0.25
  } else if (yr == "2005"| yr == "2008"){
    betaval <- 1.25
  } else if (yr == "2003" | yr == "2007"){
    betaval <- 1.5
  } else if (yr == "1998" | yr == "1999" | yr == "2002" | yr == "2010" | yr == "2011"){
    betaval <- 1.75
  } else if (yr == "2001" | yr == "2009"){
    betaval <- 2
  } else if (yr == "2000" | yr == "2004"){
    betaval <- 2.25
  }

>>>>

select month
```{r month of interest -change}
mthna <- "dec"
mthno <- "12"
```

@@

note will need to reajust background points too as some years may no longer have presence data

```{r remove na vals}
prback <- na.omit(prback)
presyrs <-  subset(prback, occurrence == 1) #this is to get years with complete presence data 
presyrs <- unique(presyrs$year) #make a vector of unique years
prback <- prback[prback$year %in% presyrs, ] #keep only the data for which there is precence years

@@

#```{r train and test inc AIC for reg val}
presyrs <-  #this is to get years with complete presence data

modelmonth <- cbind(paste0(mthna ,unique(prback$year)))
aicetc <- read.csv("../data/env/AICcCalculations.csv", header = TRUE) #pre-created csv file
betavallist <- cbind(aicetc$regularization)

@@

#```

@@

  if (yr == "1998"){
    betaval <- 0.25
  } else if (yr == "2001"){
    betaval <- 0.75
  } else if (yr == "2002" | yr == "2003"| yr == "2004"| yr == "2006"| yr == "2011"){
    betaval <- 1
  } else if (yr == "2005"){
    betaval <- 1.25
  } else if (yr == "1999" | yr == "2000"| yr == "2009"){
    betaval <- 1.5
  } else if (yr == "2007"){
    betaval <- 1.75
  } else if (yr == "2010"){
    betaval <- 2
  } else if (yr == "2008"){
    betaval <- 2.25
  }
